---
title: "STAT 428 Project: Google Stock Prediction"
author: "Group_16: Khuong Le - kmle2 (group leader), Han Sun - hansun3, Xin Sun - xins2, Xinyi Song - xinyis8, Xinye Yang - xinyey2"
date: "December 13th, 2018"
output:
  html_document:
    css: style.css
---


#**My contribution to the group project:**

I think I constribute a good amount of work to this project. As a team leader, I deliever out all the work to everyone equally and make sure our group meet every deadlines as early as possible. Firstly, I transform the data depends what the team members so that they can work on it easier. Moreover, I attend all of the group meetings and deliver out ideas on different parts to help other team members works well on their parts. Beside group meeting time, I also set time to work with Xinye Yang as we focus on the second part of our project which is  "Improving prediciton" from the first part. We divide out work equally. We were both finding  the model together and came up with the fittest one which is cubic formula. Then I work on writing some functions to transform data and check if our predict lines will fit the actual value and the predict values from first part or not. I felt that the time I spent for this projects is very useful!

#**Describe my project to interviewer:**

As a part of my class Statistical Computing, we had to do a Final Project for the class which is predicting Google stock.  As a team leader, I deliever out all the work to everyone equally and make sure everyone is on process and our group meet every deadlines as early as possible. Going into details, our projects has 2 parts, part 1 is finding models for prediction and second part is optimization that models and make sure it works properly. I worked mainly on part two with one member in group, we tried many different methods like Markov Chain, Newton Methods, Bisection and finally come up with the idea of using Leave One Out Cross-Validation to calculate Mean Square Error (MSE). At first, we find out we might fail this project because our method get only around 20% correctness. However, after optimize the method and our code, it got boost to 40% which I consider it's a success.

#**Evaluation of team member:**

 Han Sun - hansun3: 10
  Han is a really responsible team members. She always goes one step before everyone else with great ability of scheduling.  I'm very sure she contributed a certain amount of work on part one since when we worked together, she delivered out different ideas on how to improve their parts. Moreover, she also helps us on different things in our parts like which way is the fattest way to store and plot out matrix / dataframe of values. It's great to work with her.
 
 Xin Sun - xins2: 10
  Xin is really good with her plotting and visualization skills. Although she didn't talk much, she gave some good discussions on which method we should use and gave out ideas on how using it. She contributes a good amount of works on part 1, mostly on Accept / Reject method and helps team members on both part 1 and part 2. 

 
 Xinyi Song - xinyis8: 10
 Great team member! Xinyi always comes up with new cool and creative ideas to work on her part (part 1). Her knowledge is very wide since she understands nearly every distribution and knows which one to use in a certain situation. I was amazed by her Geometric Brownian Method and knowledge of Time Series. She contributed a certain amount of work in her part and also helps others. Moreover, she always did everything early and have all the work done before the deadline. If there was any questions, she didn't hesitage and asked questions to solve the problems right away.

 Xinye Yang - xinyey2: 10
 I really like to work with Xinye. Xinye attends all the meetings in our group and contribute to both part of the projects. He is the one that I worked with mostly throughout of the project since we did the second part together. He always gives first on giving out ideas what we should do and what will the result be like. He has abilities to think and solve problems really quick. I have  some problems in our part that I didn't understand and he explained me clearly and we were able to work in a quick space with not much delays.  
 
#**Journal part **
## Group Meetings:

##1. 11/02/18  at 2:30pm
(Topic: Selecting project application area and data set)

Select our topic and finding dataset online -> use Google stock dataset from Kaggle.

##2. 11/07/18 at 3:00pm 
(Topic: assign individual work to members for Project Proposal - part 1)

As a group leader, I divided the work into 2 parts:

Part1 (Group 1 method): Stock price predicting: (Han Sun(hansun3), Xin Sun(xins2), Xinyi Song(xinyis8) will focus more on this part

Part2 (Group 2 method): Improving prediciton: Khuong Le(kmle2), Xinye Yang(xinyey2) will focus more on this one.

We help each other if anyone needs help. After that, decided which packages we will use, setup code chunks so that team members can add whatever packages they want to use quick and easy. 

```{r, warning=FALSE, message=FALSE, eval=FALSE}
#Run this code block only 1 time whenever start R to get the packages installed and read!
pkg_list = c("ggplot2", "boot", "bootstrap", "tidyr", "dplyr", "stringr", "scales", "plyr", "tibble", "reshape2", "dgof", "CDFt")
mia_pkgs = pkg_list[!(pkg_list %in% installed.packages()[,"Package"])]
if(length(mia_pkgs) > 0) install.packages(mia_pkgs)
loaded_pkgs = lapply(pkg_list, require, character.only=TRUE)
```

Our dataset:

```{r, eval=FALSE}
# Setting up the dataset:
gg_stock = read.csv("gg_stock.csv")
head(gg_stock)
```

Data transforming so that we can work on the data easier.

```{r, eval=FALSE}
#Reformatting and cleaning data.
#Adding average in day and difference between open and close and also their adjusted value.
gg_stock = add_column(gg_stock, Average    = (gg_stock$High + gg_stock$Low)/2, .after = "Low")
gg_stock = add_column(gg_stock, Difference = (gg_stock$Close - gg_stock$Open), .after = "Close")
gg_stock = add_column(gg_stock, Adj..Average    = (gg_stock$Adj..High + gg_stock$Adj..Low)/2, .after = "Adj..Low")
gg_stock = add_column(gg_stock, Adj..Difference = (gg_stock$Adj..Close - gg_stock$Adj..Open), .after = "Adj..Close")
#Profit: This value returns 1 if the difference in both Difference and Adj..Difference is True, else it's 0.
for (i in 1:nrow(gg_stock)){
  if ((gg_stock$Difference[i] >= 0 && gg_stock$Adj..Difference[i] >= 0) == TRUE){
    gg_stock$Profit[i] = 1
  }
  else{
    gg_stock$Profit[i] = 0 
  }
}
#Splitting date into Day - Month -Year:

for (i in 1:nrow(gg_stock)){
  gg_stock$Day[i]   = str_split(gg_stock$Date[i], "-")[[1]][3]
  gg_stock$Month[i] = str_split(gg_stock$Date[i], "-")[[1]][2]
  gg_stock$Year[i]  = str_split(gg_stock$Date[i], "-")[[1]][1]
}
#Not  going to use Ex.Dividend and Split.Radio.
drops = c("Ex.Dividend", "Split.Ratio", "Date")
gg_stock = gg_stock[,!(names(gg_stock) %in% drops)]
gg_stock = gg_stock[c(16,17,18,seq(1,15))]
```

Deliver the Rmarkdown to team members so everyone can start contribute to the project. Each person will do one part of project for Proposal 1.

Khuong Le (kmle2): Set up dataset, transform data for easier use.

Xinyi Song(xinyis8): Overview of the data.

Xin Sun(xins2): Get the plots of the overview of data.


##3. 11/13/18 at 5:00pm
(Topic: finish and review Project Proposal - part 1; assign individual work to members for Project Proposal - part 2)

Meet up to discuss the process of doing part 1 and what to do for part 2.

##4. 11/16/18 at 3:30pm (members working on Group 1 Method)
(Topic: start working on Group 1 Method code)

For part1, we call it "Stock price predicting", we will use method like plot out several different distributions line and find the best one.
Using different ways to find out the prediction for the stock value.

1/ Basic Normal

2/  Predicting stock price for future year by Using Monte Carlo

##5. 11/27/18 at 5:00pm
(Topic: review individual work and finish Project Proposal - part 2)

For part2, we call it "Improving prediciton" plan to use MCMC or MSE or Newton methods  for optimization for the method in part 1. Then adding some code that we already finished in part 1 and write proposal Two.

##6. 12/07/18 at 3:00pm (members working on Group 1 Method)
(Topic: finish Group 1 Method code)

Get report from TA about the proposal two, so we decide to be more clear on our method by using accept - reject method to find a better distribution. Using Maximum Likelihood Estimator (MLE) to find parameters for best fit distribution. We found out that the p-value of MLE  is not sufficient so we plotted several different density curves, observing which line fit our data better and manually calculated new p-value and found out a better one to work with
After that, we add Geometric Brownian Motion Method to our prediction method.

Since part 1 data is generated mostly base on random so it's hard find the root for Newton method. Moreover, it's hard to find the transition matrix for MCMC. Then we decided to go with using Cross-Validation to calculate MSE and then testing different choose models to predict the values and compare to those methods in part 1. 

##7. 12/11/18 at 4:30pm
(Topic: Discussing process of doing Group 2 Method and fixing Group 1 method)

Planning to write the Final Group Project report for Part 1: (Han Sun(hansun3), Xin Sun(xins2), Xinyi Song(xinyis8), each person will write their report on the method that they did.

Khuong Le, Xinye Yang works together to find a good model for predicting in Group 2 Method. We try many different models like exponential, log - log, polynomial, ...

##8. 12/12/18 at 6:30pm
(Topic: Finish coding part and start to write group project report)

Part 1: Finish all the coding part and start to write report for part 1.

Part 2: Finally find out good models for calculating the prediction which is the Cubic Formula. We write many different functions to show that our lines of prediction is closed to the actual values.

Personally I write: 
"daycount": transform the data for easier use. turn vector of different days into continous day for graphing.

```{r, eval= FALSE}
daycount = function(xvalue){
ini = 0
ret = rep(0, 250)
ret[1] = xvalue[1]
for (i in 2:250){
  if(xvalue[i-1] > xvalue[i]){
    ini = ini + 1
    ret[i] = ini*30 + xvalue[i]
  }
  else{
    ret[i] = ret[i] + ini*30 + xvalue[i]
  }
}
#print(length(ret))
return (ret)
}
```


best_fit": Find distances between lines and get the smallest one.

```{r, eval= FALSE}
best_fit = function(f1, f2){
  # f1 is prediction, f2 is actual
  square_errors  = (f1 - f2)^2
  qwerty = sum(square_errors)
  return (qwerty)
}
```

##9. 12/13/18 at 9:00am
(Topic: Finish writing group project report)

Discuss on how the written report should looks like on wording, vocabuary, grammar. Then finish the project and submit files.

